---
title: "assigment_9_Aimone"
author: "Behlee Aimone"
date: "2022-10-31"
output: html_document
---

## My assigment 9

```{r}
library(tidyverse)
library(easystats)
library(dplyr)
library(kableExtra)
library(DT)
library(modelr)
```
___

```{r}
df<-read_csv("./data/GradSchool_Admissions.csv") 

```

### Here is a glimpse of our dataset
```{r}
df %>% head() %>% kable() %>% kable_classic(lightable_options = 'hover')
```
___
### Let's take a look at the relationships in this data  


```{r}
datfram<-df%>% mutate(admitancetf=case_when(admit==1~TRUE,
                        TRUE~FALSE))

p1<-datfram %>% ggplot(aes(x=gre,y=gpa,color=admitancetf))+
  geom_smooth(se=FALSE)+
  theme_minimal()
plotly::ggplotly(p1)
```


```{r}
p<-datfram %>% 
  ggplot(aes(x=gre,y=rank,color=admitancetf))+
  geom_density2d()+
  theme_minimal()
plotly::ggplotly(p)

```
#### Here is an interactive table that you can filter for attributes and see individuals that fit that criteria 
```{r}
datatable(datfram, rownames = FALSE, filter="top", options = list(pageLength = 5, scrollX=T) )
```
___
### Now let's begin to model the data 
#### First let's look how at the variables interact with eachother from 3,000 feet 
```{r}
GGally::ggpairs(datfram)
```

#### Let's make some models to attempt to explain the data 
```{r,include=TRUE}
mod1<-glm(data=datfram,
          formula = admitancetf ~ gre,
          family = "binomial")
mod2<-glm(data=datfram,
          formula = admitancetf ~ gre + gpa,
          family = "binomial")
mod3<-glm(data=datfram,
          formula = admitancetf ~ gre + gpa + rank,
          family = "binomial")
mod4<-glm(data=datfram,
          formula = admitancetf ~ gre * gpa,
          family = "binomial")
mod5<-glm(data=datfram,
          formula = admitancetf ~ gre * gpa + rank,
          family = "binomial")
compare_performance(mod1,mod2,mod3,mod4,mod5) %>% plot()
compare_performance(mod1,mod2,mod3,mod4,mod5,rank=TRUE)

add_predictions(datfram,mod5,type = "response") %>% 
  ggplot(aes(x=gre,y=pred))+
  geom_point(color="black")+
  geom_point(aes(y=admit,x=gre),alpha=.5,color="red")
# I am not sure how to make this shitty binomial data look better. 
# I think the predictions are the chance that they will get in. 

  
```
___
## This plot makes me angry, so here is a [**link**](https://www.youtube.com/watch?v=ofJHbO0plHc) to make us both feel a little better 


