---
title: "Exam 3"
author: "Behlee Aimone"
date: "2022-11-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(janitor)
library(stringr)
library(ggpubr)
library(broom)
library(AICcmodavg)
library(dplyr)
```

# 1. Load and clean FacultySalaries_1995.csv file and Re-create the graph below…
```{r}
# This is to first make the names tidy and then shift around the columns so that I can do stuff 
df<-read_csv("data/FacultySalaries_1995.csv") %>% clean_names() %>% 
  pivot_longer(c(ends_with("salary")), names_to = "rank", values_to = "salary",names_prefix = "avg_") %>% 
  pivot_longer(c(ends_with("comp")), names_to = "comp_type", values_to = "comp_amt") %>% 
  pivot_longer(c(num_full_profs,num_assoc_profs,num_assist_profs), names_to = "faculty_type", values_to = "faculty_count") %>% glimpse
```



```{r}
# first I need to get rid of the weird tier that has one data point using filter 
# then I can recreate the plot 
df %>% 
  filter(!df$tier=="VIIB") %>%
  ggplot(aes(x=rank, y=salary,fill=rank))+
  geom_boxplot()+
  facet_wrap(~tier)+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90))
```


# 2. Build an ANOVA model and display the summary output in your report.
```{r}
# I'm sure we learned this in class, but this is how I found how to do it on the internet 
# this is a model that looks at state AND rank AND tier, but NOT their interactions 
twoway<-aov(salary~state+rank+tier, data = df)
summary(twoway)
```


# 3. The rest of the test uses another data set. The “Juniper_Oils.csv” data. Get it loaded and take a look. Then tidy it! (show the code used for tidying in your report)
```{r}
# read in this bitch 
june<-read_csv("data/Juniper_Oils.csv")
# clean this hoe. Thanks for the list of names 
cleanjune<-june %>% pivot_longer(c("alpha-pinene","para-cymene","alpha-terpineol","cedr-9-ene","alpha-cedrene","beta-cedrene","cis-thujopsene","alpha-himachalene","beta-chamigrene","cuparene","compound 1","alpha-chamigrene","widdrol","cedrol","beta-acorenol","alpha-acorenol","gamma-eudesmol","beta-eudesmol","alpha-eudesmol","cedr-8-en-13-ol","cedr-8-en-15-ol","compound 2","thujopsenal"), names_to = "ChemicalID", values_to = "Concentration")
```


# 4. Make me a graph of the following:
```{r}
# make the plot 
cleanjune %>% 
  ggplot(aes(x=YearsSinceBurn, y=Concentration))+
  geom_smooth()+
  facet_wrap(~ChemicalID, scales="free")+ 
  theme_bw()
```


# 5. Use a generalized linear model to find which chemicals show concentrations that are significantly (significant, as in P < 0.05) affected by “Years Since Burn”.
```{r}
# glm of how compound and years impact concentration
mod1<-glm(data=cleanjune, 
    formula = Concentration ~ ChemicalID + YearsSinceBurn)
# this makes us a pretty little table 
tib1<-tidy(mod1, conf.level = TRUE)
# this allows me to filter out the values that don't really mean anything to me 
tib1<-tib1 %>% filter(tib1$p.value<0.05)
# now I need to get rid of the weird prefixes 
tib1 %>% transform(term=str_replace(term, "ChemicalID"," "))
 
```




